Weighted Model Counting with Conditional Probabilities

### 2020-07-15 paper.tex
A new test
Experimental results for the new non-binary encoding are somewhat encouraging

\paragraph{Experimental setup.}
\begin{itemize}
\item
  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
  \begin{itemize}
  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Encodings:
  \begin{itemize}
  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item mine
  \end{itemize}
  All except mine are from Ace
  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags.
\item Datasets\footnote{There might be more at
    \url{https://meelgroup.github.io/}.}
  \begin{itemize}
  \item binary Bayesian networks from Sang et
    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
    \cite{DBLP:conf/aaai/SangBK05}
    \begin{itemize}
    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
      deterministic),
    \item Plan recognition (problems),
    \item Deterministic quick medical reference (what do the numbers mean? the
      README doesn't say).
    \end{itemize}
  \item Bayesian networks available with Ace
    \begin{itemize}
    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06}
    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
      files have their own citation data that I should probably extract. This is
      the only dataset that has some non-binary networks.
    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06}
    \end{itemize}
  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
  \end{itemize}
\end{itemize}

@@

  tremendously, but I'm not sure if I should do that.

@@

>>>>

\paragraph{Experimental setup.}
\begin{itemize}
\item
  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
  \begin{itemize}
  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Encodings:
  \begin{itemize}
  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item mine
  \end{itemize}
  All except mine are from Ace
  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags.
\item Datasets\footnote{There might be more at
    \url{https://meelgroup.github.io/}.}
  \begin{itemize}
  \item binary Bayesian networks from Sang et
    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
    \cite{DBLP:conf/aaai/SangBK05}
    \begin{itemize}
    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
      deterministic),
    \item Plan recognition (problems),
    \item Deterministic quick medical reference (what do the numbers mean? the
      README doesn't say).
    \end{itemize}
  \item Bayesian networks available with Ace
    \begin{itemize}
    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
      files have their own citation data that I should probably extract. This is
      the only dataset that has some non-binary networks.
    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
    \end{itemize}
  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
  \end{itemize}
\end{itemize}

@@

  tremendously, but I'm not sure if I should do that. Could a heuristic do the
  same thing?

@@

\item In the encoding:
  \item We assume that the first literal after `w' is positive.
  \item The last two numbers are the positive and the negative probabilities,
    respectively---sometimes they add to one, and sometimes the negative
    probability is one, regardless of the value of the first probability.
\item My encoding for non-binary BNs should still be faster because it doesn't
  have those `equivalence' clauses.
\item Guess: what makes the problem easier is:
  \begin{enumerate}
  \item short clauses,
  \item low number of clauses.
  \end{enumerate}
  This explains why my first version of encoding non-binary CPTs was too slow.
\item With all encodings (including mine non-binary encoding), they live on a
  measure Boolean algebra where the measure is not probabilistic (so $\Pr(\neg
  A) \ne 1 - \Pr(A)$).
